\sysfull

### 2018-08-04 paper/asplos19/intro.tex
intro modified

>>>>

\todo{Add a summary of our extensive evaluations.}{Amjad, Carlo} To asses the benefits of \sys over existing task-based systems, we .... 
Our evaluation shows that \sys is $2X$ more energy-efficient than the state-of-the-art system in most cases and is able to progress where static systems fail---\emph{the only task-based system that guarantees task termination in any arbitrary task division}.
